Progress Report

### 2023-09-11 Docs/ProgressReport.Rmd
explore unidentifiability issue

---
title: "Progress Report"
author: "Ying Jin"
date: "2023-05-16"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

## Failed prediction

- Laplace approximation failed for some subjects
- Only when the observed track is short (up to 360)
- These subjects have something in common

```{r}
# compare subjects that failed at Laplace Approximation with others
rand_id <- sample(unique(df$SEQN), size = 4)
com_id <- c(rand_id, sample(skip_id, 4))

df_est_latent %>% filter(id %in% com_id) %>%
  left_join(df %>% select(SEQN, Z, sind) %>%
              rename(id = SEQN, Y=Z, bin = sind), by = c("id", "bin")) %>%
  mutate(type = ifelse(id %in% rand_id, "Prediction", "Failed prediction")) %>%
  ggplot(aes(x=bin, y=eta_hat, col = type))+
  geom_line()+
  geom_vline(xintercept = 360)+
  facet_wrap(~type+id, nrow = 2, ncol = 4)
```

## Subjects with complete prediction

```{r fig_prob, warning=FALSE}
df_est_latent %>%
  filter(id %in% rand_id) %>%
  mutate(pred_t1080 = ifelse(bin<=1080, NA, pred_t1080),
         pred_t720 = ifelse(bin<=720, NA, pred_t720),
         pred_t360 = ifelse(bin<=360, NA, pred_t360)) %>%
  mutate_at(vars(pred_t360, pred_t720, pred_t1080), function(x)exp(x)/(1+exp(x))) %>%
  left_join(df %>% select(SEQN, Z, sind) %>%
              rename(id = SEQN, Y=Z, bin = sind), by = c("id", "bin")) %>%
  ggplot()+
    geom_line(aes(x=bin, y = pred_t360, col = "360"), linetype = "dashed")+
    geom_line(aes(x=bin, y = pred_t720, col = "720"),linetype = "dashed")+
    geom_line(aes(x=bin, y = pred_t1080, col = "1080"),linetype = "dashed")+
    geom_point(aes(x=bin, y = Y, col = "Outcome"), size = 0.5)+
    facet_wrap(~id)+
    labs(x = "Time", y = "Estimated latent function (probablity scale)")
```

```{r fig_eta, warning=FALSE}
df_est_latent %>%
  filter(id %in% rand_id) %>%
  mutate(pred_t1080 = ifelse(bin<=1080, NA, pred_t1080),
         pred_t720 = ifelse(bin<=720, NA, pred_t720),
         pred_t360 = ifelse(bin<=360, NA, pred_t360)) %>%
  ggplot()+
    geom_line(aes(x=bin, y = pred_t360, col = "360"), linetype = "dashed")+
    geom_line(aes(x=bin, y = pred_t720, col = "720"),linetype = "dashed")+
    geom_line(aes(x=bin, y = pred_t1080, col = "1080"),linetype = "dashed")+
    geom_line(aes(x=bin, y = eta_hat, col = "eta_hat"), linetype = "solid" )+
    facet_wrap(~id)+
    labs(x = "Time", y = "Estimated latent function")
```

## AUC on subjects with complete prediction

- Use interpolation to fill in gaps between bins

```{r}
# subjects with complete prediction
N <- length(unique(df$SEQN))-length(skip_id)
eval_id <- setdiff(unique(df$SEQN), skip_id)
J <- max(df$sind)

# containter: row index subject, column index time
eta_mat_t360 <- eta_mat_t720 <- eta_mat_t1080 <- matrix(NA, nrow = N, ncol = J)

# interpolation
for(i in seq_along(eval_id)){
   eta_mat_t360[i, ] <- approx(x=df_est_latent$bin[df_est_latent$id==eval_id[i]],
                               y=df_est_latent$pred_t360[df_est_latent$id==eval_id[i]], 
                               xout = 1:J)$y
   eta_mat_t720[i, ] <- approx(x=df_est_latent$bin[df_est_latent$id==eval_id[i]],
                               y=df_est_latent$pred_t720[df_est_latent$id==eval_id[i]], 
                               xout = 1:J)$y
   eta_mat_t1080[i, ] <- approx(x=df_est_latent$bin[df_est_latent$id==eval_id[i]],
                               y=df_est_latent$pred_t1080[df_est_latent$id==eval_id[i]], 
                               xout = 1:J)$y
  }

@@

```{r}
# true outcome
Y_mat <- df$Z[df$SEQN %in% eval_id]
Y_mat <- matrix(Y_mat, nrow = N, ncol = J, byrow = T) 
```

```{r AUC_fGFPCA}
# maximum observations time
t_vec <- c(360, 720, 1080)

# AUC container
auc_mat <- matrix(NA, 3, 3)
colnames(auc_mat) <- c("360", "720", "1080")
rownames(auc_mat) <- c("(360, 720]", "(720, 1080]", "(1080, 1440]")

# Calculate AUC

auc_mat[1, 1] <- performance(prediction(as.vector(eta_mat_t360[, 361:720]), 
                                   as.vector(Y_mat[, 361:720])),
                        "auc")@y.values[[1]]
auc_mat[2, 1] <- performance(prediction(as.vector(eta_mat_t360[, 721:1080]), 
                                   as.vector(Y_mat[, 721:1080])),
                        "auc")@y.values[[1]]
auc_mat[3, 1] <- performance(prediction(as.vector(eta_mat_t360[, 1081:1435]), 
                                   as.vector(Y_mat[, 1081:1435])),
                        "auc")@y.values[[1]]

auc_mat[2, 2] <- performance(prediction(as.vector(eta_mat_t720[, 721:1080]), 
                                   as.vector(Y_mat[, 721:1080])),
                        "auc")@y.values[[1]]
auc_mat[3, 2] <- performance(prediction(as.vector(eta_mat_t720[, 1081:1435]), 
                                   as.vector(Y_mat[, 1081:1435])),
                        "auc")@y.values[[1]]

auc_mat[3, 3] <- performance(prediction(as.vector(eta_mat_t1080[, 1081:1435]), 
                                   as.vector(Y_mat[, 1081:1435])),
                        "auc")@y.values[[1]]
auc_mat
```

## Reference method

- GLMMadaptive?
- fcr on lowess smoothed track?

>>>>

---
title: "Progress Report"
author: "Ying Jin"
date: "2023-05-16"
output: 
  html_document:
    self_contained: no
    number_sections: true
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

## Data overview

- 8763 subjects, 1440 measures each
- no missingness

```{r}
N <- length(unique(df$SEQN)) # sample size 8763
J <- max(df$sind) # 1440 measures per subject
```

```{r}
rand_id <- sample(unique(df$SEQN), size = 4) # "toy" sample

df %>% 
  filter(SEQN %in% rand_id) %>%
  ggplot()+
  geom_point(aes(x=sind, y=Z), size = 0.5)+
  facet_wrap(~SEQN)+
  labs(x="Time", y = "Activity", title = "A brief overview of the outcome")
```

## fGFPCA Estimation

```{r}
# code
source(here("Code/GLMM-FPCA.R")) 
# use pred_latent function to estimate latent function 
source(here("Code/OutSampMLE.R"))
# source(here("Code/OutsampBayes.R"))

@@

### Binning

- Bin every 10 measures

```{r, message=FALSE}
# bin data
bin_w <- 10 # bin width
n_bin <- J/bin_w # number of bins
brks <- seq(0, J, by = bin_w) # cutoff points
mid <- (brks+bin_w/2)[1:n_bin] # mid points

df$bin <- cut(df$sind, breaks = brks, include.lowest = T, labels = mid)
df$bin <- as.numeric(as.character(df$bin))
# head(df)

df %>% 
  filter(SEQN %in% rand_id) %>%
  group_by(SEQN, bin) %>%
  summarise(num = sum(Z)) %>%
  ggplot()+
  geom_point(aes(x=bin, y=num), size = 0.5)+
  facet_wrap(~SEQN)+
  labs(x="Time", y = "Activity", title = "Number of active nimutes within each bin")
```

### Local GLMMs

- This is where near-unidentifiability issues first appear
- Though point estimation not necessarily affected

```{r, cache=TRUE, warning=FALSE}
# split by each bin
df <- df %>% rename(id = SEQN, Y=Z)
df_bin_lst <- split(df, f = df$bin)

# fit local GLMM and estimate latent function
# near-unidentifiability issues 
df_est_latent <- lapply(df_bin_lst, function(x){pred_latent(x)}) 
df_est_latent <- bind_rows(df_est_latent)

# keep midpoint values
df_est_latent <- df_est_latent %>%
  select(-sind, -Y) %>% distinct(.)
```

```{r, message=FALSE}
df %>% 
  filter(id %in% rand_id) %>%
  left_join(df_est_latent, by = c("id", "bin")) %>%
  mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=sind, y=eta_hat, group = id))+
  geom_point(aes(x=sind, y = Y, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
             alpha = 0.5, linewidth = 0.5)+
  labs(x = "Time", y = "Estimated latent function (probablity scale)")
```

```{r, message=FALSE}
# overview at estimated latent function
df %>% 
  filter(id %in% rand_id) %>%
  group_by(id, bin) %>%
  summarise(num = sum(Y)) %>%
  left_join(df_est_latent, by = c("id", "bin")) %>%
  # mutate(eta_hat = exp(eta_hat)/(1+exp(eta_hat))) %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id, linetype = "dashed"))+
  geom_point(aes(x=bin, y = num, group = id), size = 0.5)+
  facet_wrap(~id, scales = "free")+
  geom_vline(xintercept = c(465, 545, 555, 1185, 1195, 1205), col = "red",
             linewidth = 0.5, alpha = 0.6)+
  labs(x = "Bin", y = "Estimated latent function/number of active minutes")
```

- Take a closer look at the unidentifiable bins?

I just realized glmer actually used Laplace approximation as well. Could this also be due to numeric stability? In some bins (465, 545, 555, 1185, 1195, 1205), the approximation failed to converge.

Below is the warning messages and one model summary.

For this bin, the problem is with the fixed effect standard error. It is clearly near-zero.

https://www.learn-mlms.com/07-module-7.html

https://rstudio-pubs-static.s3.amazonaws.com/33653_57fc7b8e5d484c909b615d8633c01d51.html

```{r, eval=FALSE}
try_fit_lst<-list()
for(i in seq_along(df_bin_lst)){
  this_glm <- tryCatch({glmer(Y ~ 1 + (1|id), data = df_bin_lst[[i]],
                             family = binomial)},
                       warning=function(w){NA})
  try_fit_lst[[i]] <- this_glm

}

# bins where glmer returned errors
# names(df_bin_lst)[is.na(try_fit_lst)]
```

```{r}
issue_fit <- glmer(Y ~ 1 + (1|id), data = df_bin_lst[['465']],
                             family = binomial)
summary(issue_fit)

# table(df_bin_lst[['5']]$id, df_bin_lst[['5']]$Y)
```

```{r eval=FALSE}
colSums(table(df_bin_lst[['5']]$id, df_bin_lst[['5']]$Y)==0)
colSums(table(df_bin_lst[['465']]$id, df_bin_lst[['465']]$Y)==0)
```

### FPCA

```{r}
mat_est_unique <- matrix(df_est_latent$eta_hat, nrow=N, ncol=n_bin, byrow = F) 
# row index subject, column binned time
fpca_mod <- fpca.face(mat_est_unique, pve = 0.95, argvals = mid, var=T)

K <- ncol(fpca_mod$efunctions) # 18 eigenfunctions
```

```{r}
# population mean
plot(mid, fpca_mod$mu, type = "l", xlab = "bin", ylab = "mean")
```

```{r}
# eigenfunctions
par(mfrow=c(2,2))
plot(mid, fpca_mod$efunctions[, 1], type="l", xlab="bin", ylab="PC1")
plot(mid, fpca_mod$efunctions[, 2], type="l", xlab="bin", ylab="PC2")
plot(mid, fpca_mod$efunctions[, 3], type="l", xlab="bin", ylab="PC3")
plot(mid, fpca_mod$efunctions[, 4], type="l", xlab="bin", ylab="PC4")
```

```{r}
# covariance
heatmap(fpca_mod$VarMats[[which(unique(df_est_latent$id)==rand_id[1])]],
        Rowv = NA, Colv = NA, main = "Covariance matrix")
```

## Dynamic prediction

### Maximum likelihood

- Boundary hitting issues with numeric maximization
- Warning message: Steady solution not reached
- Large variation in both predicted values and scores. The numeric solution from maximum likelihood is obviously not stable. It is very likely to fail to converge.
- Perhaps it can be fixed with numeric options? But I'd rather not go that route because it depend on chance a lot.

```{r}
# Out-of-sample prediction
# maximum observations time: 360, 720, 1080
df_pred <- df_est_latent %>% filter(id %in% rand_id)
df_pred[, 'pred_t360'] <- df_pred[, 'pred_t720'] <- df_pred[, 'pred_t1080'] <- NA
score_out_mat <- array(NA, dim = c(length(rand_id), K, 3))
# dim indexes subject, eigenfunction and max obs time respectively
```

```{r, warning=FALSE}
# prediction for a single subject
for(i in rand_id){
  df_i <- df %>% filter(id==i) %>% mutate(bin=as.numeric(bin))
  # prediction
  pred_t360 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=360),
                                 fpca_fit = fpca_mod, K = K)
  pred_t720 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=720),
                                 fpca_fit = fpca_mod, K = K)
  pred_t1080 <- out_samp_dyn_pred(df_new = df_i %>% filter(sind<=1080),
                                  fpca_fit = fpca_mod, K = K)
  # prediction in container
  df_pred[df_pred$id==i, 'pred_t360'] <- pred_t360$eta_pred
  df_pred[df_pred$id==i, 'pred_t720'] <- pred_t720$eta_pred
  df_pred[df_pred$id==i, 'pred_t1080'] <- pred_t1080$eta_pred
  # score in container
  # score_out_mat[i, ,1] <- pred_t360$score_out
  # score_out_mat[i, ,2] <- pred_t720$score_out
  # score_out_mat[i, ,3] <- pred_t1440$score_out
}

```{r}
df_pred$pred_t360[df_pred$bin<=360] <- NA
df_pred$pred_t720[df_pred$bin<=720] <- NA
df_pred$pred_t1080[df_pred$bin<=1080] <- NA
# df_pred %>% filter(id == rand_id[1])
```

```{r, warning=FALSE}
df_pred %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id)
```

### Bayes method like Laplace approximation

```{r, warning=FALSE, message=FALSE, results='hide'}
df_pred2 <- df_est_latent %>% filter(id %in% rand_id)
df_pred2[, 'pred_t360'] <- df_pred2[, 'pred_t720'] <- df_pred2[, 'pred_t1080'] <- NA
score_out_mat2 <- array(NA, dim = c(length(rand_id), K, 3))

# unique id
# prediction for a single subject
source(here("Code/OutsampBayes.R"))

for(i in rand_id){
  df_i <- df %>% filter(id==i)

  # prediction 
  ## up to 360
  pred_t1 <- out_pred_laplace(fpca_mod, df_i %>% filter(sind<=360))
  eta_pred_t1 <- fpca_mod$mu+fpca_mod$efunctions%*%pred_t1$score_out
  df_pred2[df_pred2$id == i, 'pred_t360'] <- eta_pred_t1
  ## up to 720
  pred_t2 <- out_pred_laplace(fpca_mod, df_i %>% filter(sind<=720))
  eta_pred_t2 <- fpca_mod$mu+fpca_mod$efunctions%*%pred_t2$score_out
  df_pred2[df_pred2$id == i, 'pred_t720'] <- eta_pred_t2
  ## up to 1080
  pred_t3 <- out_pred_laplace(fpca_mod, df_i %>% filter(sind<=1080))
  eta_pred_t3 <- fpca_mod$mu+fpca_mod$efunctions%*%pred_t3$score_out
  df_pred2[df_pred2$id == i, 'pred_t1080'] <- eta_pred_t3

}
```

```{r}
df_pred2$pred_t360[df_pred2$bin<=360] <- NA
df_pred2$pred_t720[df_pred2$bin<=720] <- NA
df_pred2$pred_t1080[df_pred2$bin<=1080] <- NA
# df_pred %>% filter(id == rand_id[1])
```

```{r, warning=FALSE}
df_pred2 %>%
  ggplot()+
  geom_line(aes(x=bin, y=eta_hat, group = id))+
  geom_line(aes(x=bin, y = pred_t360, col = "360", group = id))+
  geom_line(aes(x=bin, y = pred_t720, col = "720", group = id))+
  geom_line(aes(x=bin, y = pred_t1080, col = "1080", group = id))+
  facet_wrap(~id)
```

<!-- ## Failed prediction  -->

<!-- - Laplace approximation failed for some subjects -->
<!-- - Only when the observed track is short (up to 360) -->
<!-- - These subjects have something in common -->

<!-- ```{r} -->
<!-- # compare subjects that failed at Laplace Approximation with others -->
<!-- rand_id <- sample(unique(df$SEQN), size = 4) -->
<!-- com_id <- c(rand_id, sample(skip_id, 4)) -->

<!-- df_est_latent %>% filter(id %in% com_id) %>% -->
<!--   left_join(df %>% select(SEQN, Z, sind) %>% -->
<!--               rename(id = SEQN, Y=Z, bin = sind), by = c("id", "bin")) %>% -->
<!--   mutate(type = ifelse(id %in% rand_id, "Prediction", "Failed prediction")) %>% -->
<!--   ggplot(aes(x=bin, y=eta_hat, col = type))+ -->
<!--   geom_line()+ -->
<!--   geom_vline(xintercept = 360)+ -->
<!--   facet_wrap(~type+id, nrow = 2, ncol = 4)+ -->
<!--   labs(y = "Estimated latend function", x = "Time", col = "") -->
<!-- ``` -->

<!-- ## Subjects with complete prediction -->

<!-- ```{r fig_prob, warning=FALSE} -->
<!-- df_est_latent %>% -->
<!--   filter(id %in% rand_id) %>% -->
<!--   mutate(pred_t1080 = ifelse(bin<=1080, NA, pred_t1080), -->
<!--          pred_t720 = ifelse(bin<=720, NA, pred_t720), -->
<!--          pred_t360 = ifelse(bin<=360, NA, pred_t360)) %>% -->
<!--   mutate_at(vars(pred_t360, pred_t720, pred_t1080), function(x)exp(x)/(1+exp(x))) %>% -->
<!--   left_join(df %>% select(SEQN, Z, sind) %>% -->
<!--               rename(id = SEQN, Y=Z, bin = sind), by = c("id", "bin")) %>% -->
<!--   ggplot()+ -->
<!--     geom_line(aes(x=bin, y = pred_t360, col = "360"), linetype = "dashed")+ -->
<!--     geom_line(aes(x=bin, y = pred_t720, col = "720"),linetype = "dashed")+ -->
<!--     geom_line(aes(x=bin, y = pred_t1080, col = "1080"),linetype = "dashed")+ -->
<!--     geom_point(aes(x=bin, y = Y, col = "Outcome"), size = 0.5)+ -->
<!--     facet_wrap(~id)+ -->
<!--     labs(x = "Time", y = "Estimated latent function (probablity scale)", -->
<!--          col = "Maximum observation time") -->
<!-- ``` -->

<!-- ```{r fig_eta, warning=FALSE} -->
<!-- df_est_latent %>% -->
<!--   filter(id %in% rand_id) %>% -->
<!--   mutate(pred_t1080 = ifelse(bin<=1080, NA, pred_t1080), -->
<!--          pred_t720 = ifelse(bin<=720, NA, pred_t720), -->
<!--          pred_t360 = ifelse(bin<=360, NA, pred_t360)) %>% -->
<!--   ggplot()+ -->
<!--     geom_line(aes(x=bin, y = pred_t360, col = "360"), linetype = "dashed")+ -->
<!--     geom_line(aes(x=bin, y = pred_t720, col = "720"),linetype = "dashed")+ -->
<!--     geom_line(aes(x=bin, y = pred_t1080, col = "1080"),linetype = "dashed")+ -->
<!--     geom_line(aes(x=bin, y = eta_hat, col = "eta_hat"), linetype = "solid" )+ -->
<!--     facet_wrap(~id)+ -->
<!--     labs(x = "Time", y = "Estimated latent function") -->
<!-- ``` -->

<!-- ## AUC on subjects with complete prediction -->

<!-- - Use interpolation to fill in gaps between bins -->

<!-- ```{r} -->
<!-- # subjects with complete prediction -->
<!-- N <- length(unique(df$SEQN))-length(skip_id) -->
<!-- eval_id <- setdiff(unique(df$SEQN), skip_id) -->
<!-- J <- max(df$sind) -->

<!-- # containter: row index subject, column index time -->
<!-- eta_mat_t360 <- eta_mat_t720 <- eta_mat_t1080 <- matrix(NA, nrow = N, ncol = J) -->

<!-- # interpolation -->
<!-- for(i in seq_along(eval_id)){ -->
<!--    eta_mat_t360[i, ] <- approx(x=df_est_latent$bin[df_est_latent$id==eval_id[i]], -->
<!--                                y=df_est_latent$pred_t360[df_est_latent$id==eval_id[i]],  -->
<!--                                xout = 1:J)$y -->
<!--    eta_mat_t720[i, ] <- approx(x=df_est_latent$bin[df_est_latent$id==eval_id[i]], -->
<!--                                y=df_est_latent$pred_t720[df_est_latent$id==eval_id[i]],  -->
<!--                                xout = 1:J)$y -->
<!--    eta_mat_t1080[i, ] <- approx(x=df_est_latent$bin[df_est_latent$id==eval_id[i]], -->
<!--                                y=df_est_latent$pred_t1080[df_est_latent$id==eval_id[i]],  -->
<!--                                xout = 1:J)$y -->
<!--   } -->

<!-- ``` -->

<!-- ```{r} -->
<!-- # true outcome -->
<!-- Y_mat <- df$Z[df$SEQN %in% eval_id] -->
<!-- Y_mat <- matrix(Y_mat, nrow = N, ncol = J, byrow = T)  -->
<!-- ``` -->

<!-- ```{r AUC_fGFPCA} -->
<!-- # maximum observations time -->
<!-- t_vec <- c(360, 720, 1080) -->

<!-- # AUC container -->
<!-- auc_mat <- matrix(NA, 3, 3) -->
<!-- colnames(auc_mat) <- c("360", "720", "1080") -->
<!-- rownames(auc_mat) <- c("(360, 720]", "(720, 1080]", "(1080, 1440]") -->

<!-- # Calculate AUC -->

<!-- auc_mat[1, 1] <- performance(prediction(as.vector(eta_mat_t360[, 361:720]),  -->
<!--                                    as.vector(Y_mat[, 361:720])), -->
<!--                         "auc")@y.values[[1]] -->
<!-- auc_mat[2, 1] <- performance(prediction(as.vector(eta_mat_t360[, 721:1080]),  -->
<!--                                    as.vector(Y_mat[, 721:1080])), -->
<!--                         "auc")@y.values[[1]] -->
<!-- auc_mat[3, 1] <- performance(prediction(as.vector(eta_mat_t360[, 1081:1435]),  -->
<!--                                    as.vector(Y_mat[, 1081:1435])), -->
<!--                         "auc")@y.values[[1]] -->

<!-- auc_mat[2, 2] <- performance(prediction(as.vector(eta_mat_t720[, 721:1080]),  -->
<!--                                    as.vector(Y_mat[, 721:1080])), -->
<!--                         "auc")@y.values[[1]] -->
<!-- auc_mat[3, 2] <- performance(prediction(as.vector(eta_mat_t720[, 1081:1435]),  -->
<!--                                    as.vector(Y_mat[, 1081:1435])), -->
<!--                         "auc")@y.values[[1]] -->

<!-- auc_mat[3, 3] <- performance(prediction(as.vector(eta_mat_t1080[, 1081:1435]),  -->
<!--                                    as.vector(Y_mat[, 1081:1435])), -->
<!--                         "auc")@y.values[[1]] -->
<!-- auc_mat -->
<!-- ``` -->

<!-- ## Reference method -->

<!-- - GLMMadaptive? -->
<!-- - fcr on lowess smoothed track? -->
